---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# menace

<!-- badges: start -->
<!-- badges: end -->

**menace** provides text-formatting tools to enhance your chat game and unleash your inner menace
(and at times, help save your coworkers from corporate depression).

## Installation

You can install this package using

``` r
# install.packages("pak")
pak::pak("adamoshen/menace")
```

or

``` r
# install.packages("remotes")
remotes::install_github("adamoshen/menace")
```

## Introduction

```{r}
library(menace)
```

**menace** works by formatting text depending on the action called. It is then up to the user to
perform any stylistic formattings and then copy the result to the clipboard, e.g. with
[**clipr**](https://matthewlincoln.net/clipr/)'s `write_clip()` function.

Designed with Microsoft Teams in mind as the output destination this package includes markup
formatters compatible with Microsoft Teams. For other destinations, consider the usage of the markup
functions contained in [**gluedown**](https://k5cents.github.io/gluedown/).

The intended use case of **menace** is for single strings. However, the functions are compatible
with character vectors.

## Example usage - `mock()`

```{r}
"This package is amazing!" |>
  mock() |>
  teams_italic()
```

## Example usage - `shout()`

```{r}
"This package is amazing!" |>
  shout() |>
  teams_bold()
```

## Example usage - `shout()` + `mock()`

```{r}
"This package is amazing!" |>
  shout() |>
  mock(method = "random") |>
  teams_bold()
```
